---
title: "Untitled"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(crosstalk)
library(leaflet)


food <- read_csv("../data/combined/foodspace_filtered_2021-08-25.csv") %>%
  arrange(name)


grocery <- food %>%
  filter(category == "grocery") %>%
  crosstalk::SharedData$new()


convenience <- food %>%
  filter(category == "convenience") %>%
  crosstalk::SharedData$new()

bakery <- food %>%
  filter(category == "bakery") %>%
  crosstalk::SharedData$new()

health_food <- food %>%
  filter(category == "health store") %>%
  crosstalk::SharedData$new()


deli <- food %>%
  filter(category == "deli meat cheese") %>%
  crosstalk::SharedData$new()

farmers_market <- food %>%
  filter(category == "farmer's market") %>%
  crosstalk::SharedData$new()

make_table <- function(data) {
  
  reactable::reactable(data,
                     filterable = FALSE,
                     searchable = TRUE,
                       selection = "multiple",
  onClick = "select",
  rowStyle = list(cursor = "pointer"),
  #defaultColDef = reactable::colDef(show = FALSE),
  columns = list(
    name = reactable::colDef(name = "Name", show = TRUE),
    address = reactable::colDef(name = "Address", show = TRUE),
    category = reactable::colDef(name = "Category", show = FALSE),
    phone = reactable::colDef(show= FALSE),
    X = reactable::colDef(show = FALSE),
    Y = reactable::colDef(show = FALSE),
    address2 = reactable::colDef(show = FALSE),
    update_date = reactable::colDef(show = FALSE),
    lat = reactable::colDef(show = FALSE),
    lng = reactable::colDef(show = FALSE),
    geometry = reactable::colDef(show = FALSE),
    note = reactable::colDef(show = FALSE)
    
  ))
}

make_map <- function(data, icon ){
  labs <-  sprintf("<b>%s</b><br>%s<br>%s", data$data()$name, data$data()$category, data$data()$address) %>%
  purrr::map(htmltools::HTML)

leaflet() %>%
  addTiles() %>%
  addAwesomeMarkers(data = data,
                    icon = icon,
                    label = labs)
}

```



Grocery {data-navmenu="Category"}
=====================================  

Column {data-width=350}
-----------------------------------------------------------------------

### Explanatory Text

Text can go here.

```{r}
#crosstalk::filter_checkbox("category",  "Category", shared_food, ~category)

```

### Interactive Data Table

```{r}
make_table(grocery)
```

Column {data-width=650}
-----------------------------------------------------------------------

### Interactive Map

```{r}

icon_carrot <- leaflet::makeAwesomeIcon(text = fontawesome::fa("fas fa-carrot"),
                                        markerColor = "green")

make_map(grocery, icon_carrot)
# 
# labs_grocery <-  sprintf("<b>%s</b><br>%s<br>%s", grocery$name, grocery$category, grocery$address) %>%
#   purrr::map(htmltools::HTML)
# 
# leaflet() %>%
#   addTiles() %>%
#   addAwesomeMarkers(data = grocery,
#                     icon = icon_carrot,
#                     label = labs_grocery)
```



Convenience {data-navmenu="Category"}
=====================================  

Column {data-width=350}
-----------------------------------------------------------------------

### Explanatory Text

Text can go here.

```{r}
#crosstalk::filter_checkbox("category",  "Category", shared_food, ~category)

```

### Interactive Data Table

```{r}
make_table(convenience)
```

Column {data-width=650}
-----------------------------------------------------------------------

### Interactive Map

```{r}
# convenience store
icon_cookie <-  leaflet::makeAwesomeIcon(text = fontawesome::fa("fas fa-cookie"),
                                                      markerColor = "blue")
make_map(convenience, icon_cookie)
```

Bakery {data-navmenu="Category"}
=====================================  

Column {data-width=350}
-----------------------------------------------------------------------

### Explanatory Text

Text can go here.

```{r}
#crosstalk::filter_checkbox("category",  "Category", shared_food, ~category)

```

### Interactive Data Table

```{r}
make_table(bakery)
```

Column {data-width=650}
-----------------------------------------------------------------------

### Interactive Map

```{r}
# bakery
icon_bread <-  leaflet::makeAwesomeIcon(text = fontawesome::fa("fas fa-bread-slice"),
                                                      markerColor = "beige")

make_map(bakery, icon_bread)
```

Health Food {data-navmenu="Category"}
=====================================  

Column {data-width=350}
-----------------------------------------------------------------------

### Explanatory Text

Text can go here.

```{r}
#crosstalk::filter_checkbox("category",  "Category", shared_food, ~category)

```

### Interactive Data Table

```{r}
make_table(health_food)
```

Column {data-width=650}
-----------------------------------------------------------------------

### Interactive Map

```{r}
# health food store
icon_leaf <- leaflet::makeAwesomeIcon(text = fontawesome::fa("fas fa-leaf"),
                                                     markerColor = "lightgreen")

make_map(health_food, icon_leaf)
```



Meat / Deli / Cheese {data-navmenu="Category"}
=====================================  

Column {data-width=350}
-----------------------------------------------------------------------

### Explanatory Text

Text can go here.

```{r}
#crosstalk::filter_checkbox("category",  "Category", shared_food, ~category)

```

### Interactive Data Table

```{r}
make_table(deli)
```

Column {data-width=650}
-----------------------------------------------------------------------

### Interactive Map

```{r}
# meat deli cheese
icon_cheese <-  leaflet::makeAwesomeIcon(text = fontawesome::fa("fas fa-cheese"),
                                                       markerColor = "orange")

make_map(deli, icon_cheese)
```



Farmer's Market {data-navmenu="Category"}
=====================================  

Column {data-width=350}
-----------------------------------------------------------------------

### Explanatory Text

Text can go here.

```{r}
#crosstalk::filter_checkbox("category",  "Category", shared_food, ~category)

```

### Interactive Data Table

```{r}
make_table(farmers_market)
```

Column {data-width=650}
-----------------------------------------------------------------------

### Interactive Map

```{r farmers_map}

# farmer's market
icon_seedling <-  leaflet::makeAwesomeIcon(text = fontawesome::fa("fas fa-seedling"),
                                                         markerColor = "darkgreen")
make_map(farmers_market, icon_seedling)
```






```{r, eval = FALSE}

# https://github.com/rstudio/leaflet/issues/691

icon_carrot <- leaflet::makeAwesomeIcon(text = fontawesome::fa("fas fa-carrot"),
                                        markerColor = "red")

# health food store
icon_leaf <- leaflet::makeAwesomeIcon(text = fontawesome::fa("fas fa-leaf"),
                                                     markerColor = "lightgreen")

# bakery
icon_bread <-  leaflet::makeAwesomeIcon(text = fontawesome::fa("fas fa-bread-slice"),
                                                      markerColor = "beige")

# convenience store
icon_cookie <-  leaflet::makeAwesomeIcon(text = fontawesome::fa("fas fa-cookie"),
                                                       markerColor = "blue")

# meat deli cheese
icon_cheese <-  leaflet::makeAwesomeIcon(text = fontawesome::fa("fas fa-cheese"),
                                                       markerColor = "orange")

# farmer's market
icon_seedling <-  leaflet::makeAwesomeIcon(text = fontawesome::fa("fas fa-seedling"),
                                                         markerColor = "darkgreen")
icon_list <- leaflet::awesomeIconList(
  "grocery" = icon_carrot,
  "farmer's market" = icon_seedling,
  "deli meat cheese" = icon_cheese,
  "convenience" = icon_cookie,
  "bakery" = icon_bread,
  "health store" = icon_leaf

)

test <- icon_list[food$category]

labs <-  sprintf("<b>%s</b><br>%s<br>%s", food$name, food$category, food$address) %>%
  purrr::map(htmltools::HTML)

leaflet() %>%
  addTiles() %>%
  addAwesomeMarkers(data = shared_food,
                    
                    icon = ~ icon_list[category]
                      # ,
                      # category == "health store" ~ icon_leaf,
                      # category == "bakery" ~ icon_bread,
                      # category == "convenience" ~ icon_cookie,
                      # category == "deli meat cheese" ~ icon_cheese,
                      # category == "farmer's market" ~ icon_seedling
                    
                    #, clusterOptions = markerClusterOptions()
                    , label = labs
                    )
                    
                    #   awesomeIcons(
                    #   library = "fa",
                    #   icon = case_when(
                    #   TRUE ~ "fas fa-carrot"
                    # )
                    #)
                    #)
# 
# leaflet() %>%
#   addTiles() %>%
#   addMarkers(data = shared_food
#              #,             clusterOptions = markerClusterOptions()
#              )
```
