---
title: "Grocery Stores in Ottawa"
output: 
  flexdashboard::flex_dashboard:
    #orientation: rows
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}

library(readr)
library(dplyr)
library(flexdashboard)
library(crosstalk)
library(leaflet)
library(DT)


ons_shp <- onsr::get_ons_shp()

grocers <- read_csv("../data/grocers_final.csv") %>%
  sf::st_as_sf(coords = c("lng", "lat"), crs = "WGS84", remove = FALSE) %>%
  group_by(lat, lng) %>%
  mutate(num = n())


grocers_ons <- onsr::get_pts_neighbourhood(pts = grocers,
                                           pgon = ons_shp) %>%
  dplyr::mutate(Name = if_else(is.na(Name), "   NA - Outside of Ottawa", Name),
                Name = purrr::map(Name, htmltools::HTML)) %>%
  sf::st_set_geometry(NULL) %>%
  select(Neighbourhood = Name,
         Name = name,
         Address = address,
         Address2 = address2,
         lng,
         lat)

labs <- paste0("<b>",grocers_ons$Name,"</b><br>",
               grocers_ons$Address,
               "<br>",grocers_ons$Address2) %>%
  purrr::map(htmltools::HTML)

sd <- crosstalk::SharedData$new(grocers_ons)
```

Column {data-height=650}
-----------------------------------------------------------------------

### 

```{r}

  leaflet() %>% 
  addTiles() %>% 
  addMarkers(data = sd, #data = grocers,
    label = labs
             #,clusterOptions = leaflet::markerClusterOptions()
             ) %>%
  addPolygons(data = ons_shp,
              weight = 2,
              fillOpacity = 0,
              label = ons_shp$Name)
  

```

Column {data-height=350}
-----------------------------------------------------------------------

### Data Table {data-height=700}


```{r, out.width="95%"}
# 
# DT::datatable(sd,
#               options = list(scrollY = TRUE,
#                              pageLength = 10,
#                              dom = "ftp",
#                              columnDefs = list(list(visible=FALSE, targets=list(5,6)))))
# 
# DT::datatable(sd,
#               extensions="Scroller", style="bootstrap", class="compact",
#               options=list(deferRender=TRUE, scrollY=300, scroller=TRUE,
#                            columnDefs = list(list(visible=FALSE, targets=list(5,6)))))
# 

DT::datatable(sd,
              style="bootstrap", class="compact",
              options=list(deferRender=TRUE, scrollY=TRUE, dom = "ftp",
                           columnDefs = list(list(visible=FALSE, targets=list(5,6)))))

```

### Additional Information

The [Ottawa Neighbourhood Study](https://www.neighbourhoodstudy.ca) (ONS) is refreshing its data about Ottawa's food environment. This data will help to understand the types of food resources available to Ottawa's residents, and can inform social policy and municipal planning.

The data shown here was collected from major food retailers' websites and from Yelp, and combined with the ONS's previous data about Ottawa's food environment.

This data is provisional: if you see any errors, or if something is missing, we would welcome your feedback via email at [ONS.eqo@gmail.com](mailto:ONS.eqo@gmail.com).

<div style="text-align: right">

*Rev 2021-06-14*

</div>